---
title: jrt – Item Response Theory Modeling and Scoring for Judgment Data
author: Nils Myszkowski
date: '2020-05-12'
slug: []
categories: [Psychometrics, Test development]
tags: []
excerpt: A package for the Psychometric analysis and scoring of judgment data using polytomous Item-Response Theory (IRT) models.
links:
- icon: r-project
  icon_pack: fab
  name: View on CRAN
  url: https://CRAN.R-project.org/package=jrt
---

# What it's about

The goal of jrt is to provide tools to use Item-Response Theory (IRT) models on judgment data, especially in the context of the Consensual Assessment Technique, as presented in Myszkowski (2021).

The goal of jrt is to provide tools to use Item-Response Theory (IRT) models on judgment data, especially in the context of the Consensual Assessment Technique, as presented in Myszkowski (2021).

* Myszkowski, N. (2021). Development of the R library "jrt": Automated item response theory procedures for judgment data and their application with the consensual assessment technique. *Psychology of Aesthetics, Creativity, and the Arts, 15*(3), 426-438. http://dx.doi.org/10.1037/aca0000287

## Vignette

The vignette can be found at https://cran.r-project.org/web/packages/jrt/vignettes/my-vignette.html



## Installation

You can install the released version of jrt from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("jrt")
```

## Example use

- Load the library

```{r}
library(jrt)
```

- Load example dataset

```{r}
data <- jrt::ratings
```

- To automatically select models 

```{r}
fit <- jrt(data, progress.bar = F, silent = T)
```

- To select models a priori

```{r}
fit <- jrt(data, irt.model = "PCM")
```

- To plot all category curves

```{r}
jcc.plot(fit)
```

- To plot one judge's category curves

```{r}
jcc.plot(fit, judge = 1)
```

- Graphical options

```{r}
jcc.plot(fit, judge = 1, overlay.reliability = T, greyscale = T, theme = "classic")
```

- To plot total information

```{r}
info.plot(fit)
```

- To plot judge information

```{r}
info.plot(fit, judge = 1)
```

- Other options for information plots

```{r}
info.plot(fit, type = "Reliability",
          y.line = .70,
          y.limits = c(0,1),
          theta.span = 4,
          theme = "classic")
```
